Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-07 lqg-strings.tex
Removed some spaces I put by habit after equations
Started EoMs section, added the dyad EoM and it's implication for the form of the dyad

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
\begin{equation}\label{eqn:lqg-string-action}
	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E_{\mu} ^{I} E_{\nu I} ,
\end{equation}
where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{align}\label{eqn:worldsheet-deriv}
	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} \ , \\
	D_{a} v^{i}      & = \partial _{a} v^{i} + \omega ^{i} _{a j} v^{j} \ ,
\end{align}
where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

@@

>>>>

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
\begin{equation}\label{eqn:lqg-string-action}
	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E_{\mu} ^{I} E_{\nu I} ,
\end{equation}
where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{align}\label{eqn:worldsheet-deriv}
	D_a X^{\mu} _{i} & = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} , \\
	D_{a} v^{i}      & = \partial _{a} v^{i} + \omega ^{i} _{a j} v^{j} ,
\end{align}
where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

@@

\subsection{The Dyad Equation}\label{subsec:dyad-eom}

Variation of the modified Polyakov action(\ref{eqn:lqg-string-action}) w.r.t the zweibein $e^{c} _{k}$ yields the vanishing of the Lie algebra-valued energy-momentum tensor, which can be contracted with the dyad to yield the regular stress-energy tensor:
\begin{equation} \label{eqn:variation-wrt-e}
	\frac{\delta S_{PA}}{\delta e^{c} _{k}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:vanishing-em-tensor}
	T^{k} _{c} := E^{I} _{\mu} E_{\nu I} (e^{a k} D_{a} \Tilde{X}^{\mu} D_{c} \Tilde{X}^{\nu} -
\end{equation}
\begin{equation*}
	- e^{k} _{c} e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu}) = 0 .
\end{equation*}
Equation(\ref{eqn:vanishing-em-tensor}) can be used to obtain an expression for the dyads in terms of the string coordinates $\Tilde{X}^{\mu}$ as in
\begin{equation} \label{eqn:dyad-string-coordinates}
	e^{k} _{c} = F e^{a k} D_{a} \Tilde{X}^{\mu} D_{c} \Tilde{X}^{\nu} E^{I} _{\mu} E_{\nu I} ,
\end{equation}
where the function $F$ is given by
\begin{equation} \label{eqn:F-function-dyad}
	\frac{1}{F} = e^{a} _{i} e^{b i} D_{a} \Tilde{X}^{\mu} D_{b} \Tilde{X}^{\nu} E^{I} _{\mu} E_{\nu I} .
\end{equation}
